MS Prelim Data K23

### 2024-07-17 scripts/first_pass_adapting_K23_analysis_20231031.Rmd
All sorts of gams

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(visreg)
library(lme4)
library(lmerTest)
library(ggplot2)
library(reshape2)
library(pwr)
library(mgcv)
library(stringr)
library(MatchIt)
library(ggpubr)
#functions
source("~/BBL/msanxiety/scripts/ms_functions.R")
```

@@

#n=867
df_people_with_good_mimosa <- data_2023_pull %>% 
  group_by(EMPI, EXAM_DATE) %>%
  slice(1) %>%
  left_join(mimosa_unique_score_gre_75, by = c("EMPI", "EXAM_DATE")) %>%
  filter(!is.na(score))
```

@@

#COLLAPSE anxiety dx and antianxiety meds with those plus depression, and anxiety dx OR on anxiety meds into 1 group -->> THIS IS THE MONEY
```{r group_anxietydx_meds_and_dep_comorbidity}
#this collapses anxiety group + meds with those with anxiety group + meds + with/without depression

@@

  #mean disease by anxiety dose: anxiety_dose  0.03606    0.01493   2.416   0.0162 *
  anxietyGrouping_mean_disease_lm <- lm(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
  summary(anxietyGrouping_mean_disease_lm)

  ### gam instead
    anxietyGrouping_mean_disease_gam <- gam(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
  summary(anxietyGrouping_mean_disease_gam)

@@

  #gam: anxiety_dose  0.03692    0.01496   2.468    0.014 *  
      anxietyGrouping_by_sex_mean_disease_gam <- gam(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose + osex+ s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
      summary(anxietyGrouping_by_sex_mean_disease_gam)

@@

  #gam
   anxietyGrouping_anxiety_net_gam<- gam(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
  summary(anxietyGrouping_anxiety_net_gam)

  #volume lost in anxiety net by anxiety dose*sex: anxiety_dose         0.053407   0.021365   2.500   0.0129 *  
  anxietyGrouping_by_sex_anxiety_net_lm <- lm(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose*osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
  summary(anxietyGrouping_by_sex_anxiety_net_lm)

  #gam
  anxietyGrouping_by_sex_anxiety_net_gam <- gam(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose*osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
  summary(anxietyGrouping_by_sex_anxiety_net_gam)

@@

  #gam
   anxietyGrouping_cov_sex_anxiety_net_gam <- gam(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
  summary(anxietyGrouping_cov_sex_anxiety_net_gam)

########UF R - just looking at uncinate by anxiety dose; anxiety_dose      369.72     187.93   1.967   0.0499 *  ***********
  anxietyGrouping_UF_R_lm <- lm(UF_R_vol ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
  summary(anxietyGrouping_UF_R_lm)

@@

   #gam, anxiety_dose    229.9      133.9   1.717   0.0868 .  
  anxietyGrouping_UF_L_by_sex_gam <- gam(UF_L_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
  summary(anxietyGrouping_UF_L_by_sex_gam)

  #burden of anxiety by network
  #clean up data frame
  df_empi_dx_network_proportions <- df_demo_and_fascicles %>%
  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == c("true_healthy", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")) %>% 
  mutate(subject = as.factor(EMPI)) %>%
  mutate(Diagnosis = oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
  mutate(Diagnosis = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy", "MS-Anxiety", "MS+Anxiety")) %>%
  mutate(Diagnosis = as.factor(Diagnosis)) %>%
  mutate(Anxiety_network = proportion_volume_lost_anxiety_net_by_network_size_sum_top_25) %>%
  mutate(Nonanxiety_network = proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75) %>%
  dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, PAT_AGE_AT_EXAM, UF_R_vol, UF_L_vol) %>% 
  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex, -UF_R_vol, -UF_L_vol) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
  mutate(Network = as.factor(Network)) %>%
  ungroup()

@@

#do lm UF*Diagnosis
 #UF_R_vol -> DiagnosisMS+Anxiety  1406.32     350.74   4.010 8.81e-05 ***
disease_UF_R_vol_lm <- lm(UF_R_vol ~ Diagnosis + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
summary(disease_UF_R_vol_lm)

 #UF_L_vol -> DiagnosisMS+Anxiety   728.93     249.71   2.919  0.00395 ** 
disease_UF_L_vol_lm <- lm(UF_L_vol ~ Diagnosis + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
summary(disease_UF_L_vol_lm)

############## sex diff
#df_anxiety_disorder_by_sex <-

## net by sex

@@

@@

@@

#gam
diagnosis_by_age_gam <- gam(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose+s(PAT_AGE_AT_EXAM, by = anxiety_dose), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
summary(diagnosis_by_age_gam)
summary(diagnosis_by_age_gam)$s.table
plot(diagnosis_by_age_gam)

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(dplyr)
library(visreg)
library(lme4)
library(lmerTest)
library(ggplot2)
library(reshape2)
library(pwr)
library(mgcv)
library(stringr)
library(MatchIt)
library(ggpubr)
library(tidymv)
#functions
source("~/BBL/msanxiety/scripts/ms_functions.R")
```

@@

#n=867, individual scans
df_people_with_good_mimosa <- data_2023_pull %>% 
  group_by(EMPI, EXAM_DATE) %>%
  slice(1) %>%
  left_join(mimosa_unique_score_gre_75, by = c("EMPI", "EXAM_DATE")) %>%
  filter(!is.na(score))
```

@@

#COLLAPSE anxiety dx and antianxiety meds with those plus depression, and anxiety dx OR on anxiety meds into 1 group -->> THIS IS THE MONEY
### Overlap with depression group
```{r overlap_with_dep_group}

#read csv of empis from depression paper
depression_empis <- read.table(file="/Users/eballer/BBL/msanxiety/data/empis_of_people_in_BP_depression_paper.csv")
names(depression_empis) <- "EMPI"

#get final anxiety dataset and make column if the empi is in the prev list
df_disease_burden_unc_and_anx_net_collapsed_variables <- df_demo_and_fascicles %>%
  mutate(EMPI = as.numeric(EMPI)) %>%
  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
  mutate(EMPI_in_dep_group = EMPI %in% depression_empis$EMPI)

 tibble_overall_counts <- df_disease_burden_unc_and_anx_net_collapsed_variables %>% 
  group_by(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
  summarize(n(),
            num_in_dep_group = sum(EMPI_in_dep_group),
            percent_overlap = num_in_dep_group/n())
 tibble_overall_counts

```
### Overall Disease by Anxiety Dose *acnp
```{r group_anxietydx_meds_and_dep_comorbidity}
#this collapses anxiety group + meds with those with anxiety group + meds + with/without depression

@@

  #mean disease by anxiety dose: anxiety_dose    0.0347504  0.0149813   2.320  0.02091 *  
  anxietyGrouping_mean_disease_lm <- lm(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
  summary(anxietyGrouping_mean_disease_lm)

  ### gam instead, anxiety_dose  0.03606    0.01493   2.416   0.0162 *
    anxietyGrouping_mean_disease_gam <- gam(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
  summary(anxietyGrouping_mean_disease_gam)

@@

  #gam: anxiety_dose  0.03692    0.01496   2.468    0.014 *  
      anxietyGrouping_by_sex_mean_disease_gam <- gam(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose + osex+ s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
      summary(anxietyGrouping_by_sex_mean_disease_gam)
```

### Anxiety network by anxiety dose
```{r}

#define group
df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
  filter (anxiety_dose != 3)

@@

  #gam, anxiety_dose  0.03735    0.01760   2.122   0.0345 * 
   anxietyGrouping_anxiety_net_gam<- gam(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
  summary(anxietyGrouping_anxiety_net_gam)

  #volume lost in anxiety net by anxiety dose*sex: anxiety_dose         0.053407   0.021365   2.500   0.0129 *  , no intx
  anxietyGrouping_by_sex_anxiety_net_lm <- lm(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose*osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
  summary(anxietyGrouping_by_sex_anxiety_net_lm)

  #gam, anxiety_dose         0.05395    0.02133   2.529   0.0119 *  
  anxietyGrouping_by_sex_anxiety_net_gam <- gam(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose*osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
  summary(anxietyGrouping_by_sex_anxiety_net_gam)

@@

  #gam, anxiety_dose  0.03810    0.01765   2.159   0.0315 * 
   anxietyGrouping_cov_sex_anxiety_net_gam <- gam(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
  summary(anxietyGrouping_cov_sex_anxiety_net_gam)

### NonAnxiety network by anxiety dose
```{r}

#define group
df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
  filter (anxiety_dose != 3)

  ###  anxiety_dose: anxiety_dose    0.0334038  0.0135143   2.472   0.0139 * 
  anxietyGrouping_nonanxiety_net_lm <- lm(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
  summary(anxietyGrouping_nonanxiety_net_lm)

  #gam, anxiety_dose  , anxiety_dose  0.03505    0.01340   2.616  0.00927 ** 
   anxietyGrouping_nonanxiety_net_gam<- gam(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
  summary(anxietyGrouping_nonanxiety_net_gam)

  #volume lost in anxiety net by anxiety dose*sex: anxiety_dose         0.0459425  0.0164036   2.801  0.00537 ** 
  anxietyGrouping_by_sex_nonanxiety_net_lm <- lm(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose*osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
  summary(anxietyGrouping_by_sex_nonanxiety_net_lm)

  #gam, anxiety_dose, anxiety_dose         0.047100   0.016230   2.902  0.00393 **          
  anxietyGrouping_by_sex_nonanxiety_net_gam <- gam(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose*osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
  summary(anxietyGrouping_by_sex_nonanxiety_net_gam)

  #volume lost in anxiety net by anxiety dose + sex + PAT_AGE_AT_EXAM: anxiety_dose     0.0344065  0.0135309   2.543   0.0114 *  
  anxietyGrouping_cov_sex_nonanxiety_net_lm <- lm(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose + osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
  summary(anxietyGrouping_cov_sex_nonanxiety_net_lm)

  #gam, anxiety_dose - anxiety_dose  0.03600    0.01342   2.682  0.00764 ** 
   anxietyGrouping_cov_sex_nonanxiety_net_gam <- gam(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
  summary(anxietyGrouping_cov_sex_nonanxiety_net_gam)

###Check for polynomial relationships 
```{r polynomial_relationships}
 #Not finding them w healthy, anxietydx OR meds, anxiety AND meds

 #check for polynomial relationship
#define group
df_demo_and_fascicles_no_unclass_anxiety_dose_factor <- df_demo_and_fascicles %>%
  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
  filter (anxiety_dose != 3) %>% 
  mutate(anxiety_dose = as.factor(anxiety_dose))

contrasts(df_demo_and_fascicles_no_unclass_anxiety_dose_factor$anxiety_dose) <- contr.poly(3)

# Perform Anova across all regions, anxiety_dose      2  0.195  0.0975   2.508  0.0829 .  
anova_result_contrasts_whole_brain <- aov(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose + PAT_AGE_AT_EXAM + osex, data = df_demo_and_fascicles_no_unclass_anxiety_dose_factor)
summary(anova_result_contrasts_whole_brain)

# Perform ANOVA again with contrasts anxiety net, anxiety_dose      2  0.216  0.1079   2.012 0.135161    
anova_result_contrasts_anxiety_net <- aov(proportion_volume_lost_anxiety_net_by_network_size_sum_top_25 ~ anxiety_dose + PAT_AGE_AT_EXAM + osex, data = df_demo_and_fascicles_no_unclass_anxiety_dose_factor)
summary(anova_result_contrasts_anxiety_net)

# Nonanxiety Net - anxiety_dose      2  0.180  0.0898   2.842   0.0596 . 
anova_result_contrasts_nonanxiety_net <- aov(proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75 ~ anxiety_dose + PAT_AGE_AT_EXAM + osex, data = df_demo_and_fascicles_no_unclass_anxiety_dose_factor)
summary(anova_result_contrasts_nonanxiety_net)

#UF_R_vol, anxiety_dose      2 2.219e+07  11094236   1.811    0.165

anova_result_contrasts_UF_R_net <- aov(UF_R_vol ~ anxiety_dose + PAT_AGE_AT_EXAM + osex, data = df_demo_and_fascicles_no_unclass_anxiety_dose_factor)
summary(anova_result_contrasts_UF_R_net)

#UF_L_vol, anxiety_dose      2 6.053e+06  3026730   0.988    0.373  
anova_result_contrasts_UF_L_net <- aov(UF_L_vol ~ anxiety_dose + PAT_AGE_AT_EXAM + osex, data = df_demo_and_fascicles_no_unclass_anxiety_dose_factor)
summary(anova_result_contrasts_UF_L_net)

### Uncinate by Anxiety Dose *acnp?
```{r uncinateByAnxietyDose}

#results: Anxiety dose related to UF_R when covarying for linear effects of age and sex, just barely

#define group
df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
  filter (anxiety_dose != 3)

########UF R - just looking at uncinate by anxiety dose; anxiety_dose      369.72     187.93   1.967   0.0499 *  *********** (LINEAR AGE)
  anxietyGrouping_UF_R_lm <- lm(UF_R_vol ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
  summary(anxietyGrouping_UF_R_lm)

@@

   #gam, anxiety_dose    229.9      133.9   1.717   0.0868 .  
  anxietyGrouping_UF_L_by_sex_gam <- gam(UF_L_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
  summary(anxietyGrouping_UF_L_by_sex_gam)
```

##### Laterality in uncinate
```{r laterality}
  #laterality 
  #overall - t = -11.597, df = 1322.2, p-value < 2.2e-16
  right_vs_left_uncinate <- t.test(df_demo_and_fascicles_no_unclass_anxiety_dose$UF_L_vol, df_demo_and_fascicles_no_unclass_anxiety_dose$UF_R_vol)
  print(right_vs_left_uncinate)

  #healthy - t = -6.3298, df = 347.5, p-value = 7.577e-10
   right_vs_left_uncinate_healthy <- t.test(df_demo_and_fascicles_no_unclass_anxiety_dose$UF_L_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 0], df_demo_and_fascicles_no_unclass_anxiety_dose$UF_R_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 0])
  print(right_vs_left_uncinate_healthy)

  #anxietydx or meds - t = -7.7742, df = 705.18, p-value = 2.694e-14
  right_vs_left_uncinate_anxiety_or_meds <- t.test(df_demo_and_fascicles_no_unclass_anxiety_dose$UF_L_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 1], df_demo_and_fascicles_no_unclass_anxiety_dose$UF_R_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 1])
  print(right_vs_left_uncinate_anxiety_or_meds)

  #anxious+meds, t = -5.9638, df = 266.42, p-value = 7.804e-09
   right_vs_left_uncinate_anxiety_and_meds <- t.test(df_demo_and_fascicles_no_unclass_anxiety_dose$UF_L_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 2], df_demo_and_fascicles_no_unclass_anxiety_dose$UF_R_vol[df_demo_and_fascicles_no_unclass_anxiety_dose$anxiety_dose == 2])
  print(right_vs_left_uncinate_anxiety_and_meds)
```

### Fornix by Anxiety Dose
```{r uncinateByAnxietyDose}

#results: Anxiety dose NOT related to F_R when covarying for linear effects of age and sex, not in line with that one paper that found fornix differences

#define group
df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
  filter (anxiety_dose != 3)

########UF R - just looking at fornix by anxiety dose -NS
  anxietyGrouping_F_R_lm <- lm(F_R_vol ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
  summary(anxietyGrouping_F_R_lm)

  #gam, anxiety_dose    - NS
  anxietyGrouping_F_R_gam <- gam(F_R_vol ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
  summary(anxietyGrouping_F_R_gam)

  #UF _ R anxiety_dose     - NS    
  anxietyGrouping_F_R_by_sex_lm <- lm(F_R_vol ~ anxiety_dose + osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
  summary(anxietyGrouping_F_R_by_sex_lm)

  #gam, anxiety_dose  - NS 
    anxietyGrouping_F_R_by_sex_gam <- gam(F_R_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
  summary(anxietyGrouping_F_R_by_sex_gam)

  #UF L - anxiety_dose    - NS 
  anxietyGrouping_F_L_lm <- lm(F_L_vol ~ anxiety_dose + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
  summary(anxietyGrouping_F_L_lm)

   #gam, anxiety_dose    - NS  
  anxietyGrouping_F_L_gam <- gam(F_L_vol ~ anxiety_dose + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
  summary(anxietyGrouping_F_L_gam)

  #F_L anxiety_dose:NS        
  anxietyGrouping_F_L_by_sex_lm <- lm(F_L_vol ~ anxiety_dose + osex + PAT_AGE_AT_EXAM, data=df_demo_and_fascicles_no_unclass_anxiety_dose)
  summary(anxietyGrouping_F_L_by_sex_lm)

   #gam, anxiety_dose - NS
  anxietyGrouping_F_L_by_sex_gam <- gam(F_L_vol ~ anxiety_dose + osex + s(PAT_AGE_AT_EXAM, k = 4, fx = T), data=df_demo_and_fascicles_no_unclass_anxiety_dose)
  summary(anxietyGrouping_F_L_by_sex_gam)
```

### Network*Diagnosis
```{r networkxdiagnosis_groups_collapse}

## take home: comparing healthy to has anxiety AND meds, more disease within vs outside net, anxiety vs non, no interaction.
## take home #2 : More disease in R & L uncinate in anxious versus nonanxious

  #burden of anxiety by network
  #clean up data frame
  df_empi_dx_network_proportions <- df_demo_and_fascicles %>%
  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed == c("true_healthy", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")) %>% 
  mutate(subject = as.factor(EMPI)) %>%
  mutate(Diagnosis = oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
  mutate(Diagnosis = ifelse(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed=="true_healthy", "MS-Anxiety", "MS+Anxiety")) %>%
  mutate(Diagnosis = as.factor(Diagnosis)) %>%
  mutate(Anxiety_network = proportion_volume_lost_anxiety_net_by_network_size_sum_top_25) %>%
  mutate(Nonanxiety_network = proportion_volume_lost_nonanxiety_net_by_network_size_sum_bottom_75) %>%
  dplyr::select(subject, osex, Diagnosis, Anxiety_network, Nonanxiety_network, PAT_AGE_AT_EXAM, UF_R_vol, UF_L_vol, F_R_vol, F_L_vol) %>% 
  gather(Network, proportion_affected, -subject, -Diagnosis, -PAT_AGE_AT_EXAM, -osex, -UF_R_vol, -UF_L_vol, -F_R_vol, -F_L_vol) %>% #this is like a melt. Keeps empi and depGroupVar out of the melt
  mutate(Network = as.factor(Network)) %>%
  ungroup()

@@

#do lm UF*Diagnosis
 #UF_R_vol -> DiagnosisMS+Anxiety  1418.26     352.04   4.029 8.20e-05 ***
disease_UF_R_vol_lm <- lm(UF_R_vol ~ Diagnosis + osex + PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
summary(disease_UF_R_vol_lm)

 #UF_L_vol -> DiagnosisMS+Anxiety   737.97     250.61   2.945  0.00365 ** 
disease_UF_L_vol_lm <- lm(UF_L_vol ~ Diagnosis + osex+PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
summary(disease_UF_L_vol_lm)

#Fornix - Right side but not left
 #F_R_vol -> DiagnosisMS+Anxiety   860.50     368.16   2.337   0.0205 * 
disease_F_R_vol_lm <- lm(F_R_vol ~ Diagnosis + osex+ PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
summary(disease_F_R_vol_lm)

 #F_L_vol -> DiagnosisMS+Anxiety  329.724    181.609   1.816   0.0711 . 
disease_F_L_vol_lm <- lm(F_L_vol ~ Diagnosis + osex+ PAT_AGE_AT_EXAM, data = df_empi_dx_network_proportions)
summary(disease_F_L_vol_lm)
## net by sex

@@

### Diag Effect Size * Fascicle anxiety net overlap (from depression analysis) - NOT SIG both vol and prop, only vol shown here
```{r dxEffSizeOverlapwithAnxietyNet}
#define group
df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
  mutate(anxiousAndMeds_or_healthy = oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed) %>%
  filter(anxiousAndMeds_or_healthy %in% c("true_healthy", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")) %>%
  mutate(anxiousAndMeds_or_healthy = factor(anxiousAndMeds_or_healthy, levels=c("true_healthy", "Has.Anxiety.And.On.Anxiety.Meds.Inc.Dep")))

#Positive Ts are places where anxious people have more disease than controls
fascicle_anxiety_vs_healthy_effsize <- sapply(fascicle_names_w_vol_suffix, function(fascicle) 
{

  text_for_eval <- paste0("rstatix::wilcox_effsize(df_demo_and_fascicles_no_unclass_anxiety_dose, formula = ", fascicle, " ~ anxiousAndMeds_or_healthy, paired = F, conf.level = 0.95, ci.type = \"perc\", nboot = 1000)$effsize")
  eval(parse(text=text_for_eval))
})
names(fascicle_anxiety_vs_healthy_effsize) <- fascicle_names_w_vol_suffix

#convert to data frame
df_effsize_values <- as.data.frame(fascicle_anxiety_vs_healthy_effsize)

#write.table(x = df_effsize_values, file = paste0(homedir, "results/fascicle_and_wilcox_effect_size_for_volxdx_analysis_n77.csv"), row.names = T, col.names = F, quote = F, sep = ",")

#### Plot effect size x Anxiety net overlap - N.S. (including if I drop all fascicles with no overlap)
``` {r plot_scatter}
#######################
### plot differences ##
#######################

#combine data frames, column 1 has names of fascicles, column 2 has Volume of overlap with anxiety network, column 3 has t-test value of anxiety vs healthy unc, 4th anxiety vs healthy fdr corrected within that fascicle

df_fascicle_anxiety_mask_volume_overlap_effsize_value <- data.frame(neurosynth_anxiety_network_fascicle_overlap$fascicle, neurosynth_anxiety_network_fascicle_overlap$non_zero_voxels_in_anxiety_map, df_effsize_values)
names(df_fascicle_anxiety_mask_volume_overlap_effsize_value) <- c("fascicle", "volume_in_anxiety_mask", "anxiety_vs_healthy_effsize")

#remove values that have no overlap
#df_fascicle_anxiety_mask_volume_overlap_effsize_value <- df_fascicle_anxiety_mask_volume_overlap_effsize_value

# plot fascicle overlap x Eff size value
#statistic, 
anxiety_overlap_x_anxiety_vs_healthy_vol_effsize <- lm(anxiety_vs_healthy_effsize ~ volume_in_anxiety_mask, data=df_fascicle_anxiety_mask_volume_overlap_effsize_value )
summary(anxiety_overlap_x_anxiety_vs_healthy_vol_effsize)

scatter_effsize_val_by_anxiety_net_overlap_log <- ggplot(data=df_fascicle_anxiety_mask_volume_overlap_effsize_value, aes(x=volume_in_anxiety_mask, y=anxiety_vs_healthy_effsize, color=anxiety_vs_healthy_effsize)) +
  geom_point(size=2) + 
  scale_color_gradient(low = "#FFFFFF", high = "#ff00ff") +
  geom_smooth(formula = y ~ x, method=lm, color="black")+
  scale_x_continuous(trans=scales::pseudo_log_trans(base = 10), breaks=c(0, 10, 100, 1000, 10000, 100000)) + 
  xlab("Volume of Fascicle in Anxiety Network") + 
  ylab("Effect Size (r)") + 
  theme(plot.title=element_text(hjust=0.5),
        axis.text = element_text(size=16, color = "black"),
        axis.title = element_text(size=18, color = "black"),
        axis.line = element_line(color="black", size=1.3),
        panel.background = element_blank(),
        legend.position = "none",
        aspect.ratio = 4/4) + 
  annotate("text", x=1.6, y=0.14, size = 5, 
           label = paste0("P = ", round(summary(anxiety_overlap_x_anxiety_vs_healthy_vol_effsize)$coef[2,4],2)))

print(scatter_effsize_val_by_anxiety_net_overlap_log)

#save as pdf
#pdf(file=paste0(homedir, "/results/Figures_for_msanxietyn_paper/scatter_effsize_val_by_anxiety_net_overlap_log.pdf"))
 # scatter_effsize_val_by_anxiety_net_overlap_log
#dev.off()

#df_for_making_colors <- df_fascicle_anxiety_mask_volume_overlap_effsize_value %>% dplyr::select(fascicle, anxiety_vs_healthy_effsize)
#write.table(x = df_for_making_colors, file = paste0(homedir, "results/fascicle_and_effect_size_for_volxdx_analysis_n77.csv"), row.names = F, col.names = F, quote = F, sep = ",")

### Sex Differences
```{r diseaseXsexdiff}
############## sex diff
#df_anxiety_disorder_by_sex <-

#define group
df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
  filter (anxiety_dose != 3)

@@

### Age*Disease
```{r diagnosisXage}

#define group
df_demo_and_fascicles_no_unclass_anxiety_dose <- df_demo_and_fascicles %>%
  filter(oanxietydx_OR_meds_AND_Anxietydx.Meds.And.Dep.True.Healthy.Collapsed != "unclassified") %>%
  filter(anxiety_dose != 3) %>%
  mutate(anxiety_dose_factor = ordered(anxiety_dose))

@@

#gam dose
diagnosis_by_age_gam <- gam(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose+s(PAT_AGE_AT_EXAM, by = anxiety_dose), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
summary(diagnosis_by_age_gam)
summary(diagnosis_by_age_gam)$s.table
#plot(diagnosis_by_age_gam)

#gam factor - there is a linear dose effect per network size sum, as well as a sig age by anxiety relationship, but only in sick people
diagnosis_by_age_gam_factor <- gam(proportion_volume_lost_per_total_network_size_sum ~ anxiety_dose_factor+s(PAT_AGE_AT_EXAM, by = anxiety_dose_factor), data = df_demo_and_fascicles_no_unclass_anxiety_dose, method = "REML")
summary(diagnosis_by_age_gam_factor)
summary(diagnosis_by_age_gam_factor)$s.table
#plot(diagnosis_by_age_gam_factor)
